### 2018-04-30 paper/squad-overlay-design.tex
up

we need a probabilistic model of the user's behavior to predict its future activity.
In \name, the only data we collect are the availability times of each device.
In this section only, we discretize time. 
We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
Our goal is to predict $O_{t+1}$ knowing $O_t$.

>>>>

we need a probabilistic model of the user's behavior to predict its future activity.
In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
In our model, time is discretized, i.e. users periodically change the availability stated of their devices in a predefined period.
We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
Our goal is to predict $O_{t+1}$ knowing $O_t$.
